%!TEX root = ../Thesis.tex
\chapter{Acknowledgements}
\label{sec:acknowledgements}

Carrying out this PhD work has been both challenging and rewarding, and I have grown throughout it- both professionally and personally. This achievement would not have been possible without the immense amount of guidance and support I have received along the way. Firstly I would like to recognize my supervisor Mike, who has provided me with an outstanding level of encouragement complemented with productive mentorship of the highest standard. Similarly my co-supervisor Nikos for our many fruitful discussions, and for his services as PhD coordinator. My section leaders Hans and Poul, who have given me freedom and opportunity to pursue new ideas and for including me on equal terms within the institute. And all of my colleagues at DTU Wind Energy who I have exchanged ideas with and in many cases befriended. Working alongside fellow PhD students Tobias, Jonas, Pedro and Dominique has been especially gratifying in that regard. My hosts Sue and David-John and all the wonderful people I met during my stay at NCAR have also been extremely helpful and made my time in Boulder a real highlight. It was also a pleasure teaching together with Pierre in the Renewables in Electricity Markets course, and collaborating with the WFCT and WISDOM project partners. Further, I have greatly enjoyed the many conferences I attended, and would like to thank both the organizers and attendees I have interacted with for their valuable feedback.

The experimental component of this project has been greatly aided through the actions of a number of colleagues. I would like to sincerely thank Guillaume for everything he has taught me about how to design, build, and repair lidar systems, and for his invaluable assistance with the field campaigns. Likewise Nikola who has helped immensely in developing my knowledge and experience in the science of measurements. The technical staff at DTU have been an invaluable resource, and I would like to express my appreciation to Per, Steen and Hector. The coding and data analysis portion has heavily relied upon open-source software, and sincere thanks are due to all the contributing developers for their time and effort.

Funding for this PhD project has been generously provided by the department through the Danish taxpayers and industry partners. The Otto M{\o}nsted Fund has also kindly financed a portion of the external research stay costs. I would also like to thank those who have had direct contributions to this thesis. Antoine for sharing his \LaTeX template, Charlotte for translating the Danish summary, and the examination committee (Rozenn, Lars, and Hannele) for reading and evaluating this body of work.

Last but certainly not least, I  my eternal appreciation to my extraordinary family who have given me unbounded love and support and encouraged my drive to learn and experience the world.

%I am very fortunate to have  in life.
%I could ask for nothing more out of life.

\begin{comment}
\end{comment}
