%!TEX root = ../Thesis.tex
\chapter{Thesis outline and list of publications}
\label{sec:outline}


This thesis consists of a synopsis providing context for the work undertaken, a collaborative review paper of the state of the art in the field and two results papers which form the basis for the novel discoveries made during the PhD project. The papers are connected by various supporting chapters, addendums and case studies. In the end, a discussion and outlook chapter reflects on the key findings and recommends a practical approach for future work in the field. Following this, overall conclusions of the thesis are presented.
\\\\
The following three articles are included, with permission from the copyright holders where applicable. 
\\\\
Other publications produced during the PhD period but outside the scope of this thesis are not considered.
\\
\begin{enumerate}
    \item W\"urth, I., Valldecabres, L., Simon, E., M\"ohrlen, C., Uzuno\u glu, B., Gilbert, C., Giebel, G., and Kaifel, A.: Minute-Scale Forecasting of Wind Power - Results from the collaborative workshop of IEA Wind Task 32 and 36, Energies, in review, 2018.
    
    \item Simon, E., Courtney, M., and Vasiljevic, N.: Minute-Scale Wind Speed Forecasting Using Scanning Lidar Inflow Measurements, Wind Energ. Sci. Discuss., https://doi.org/10.5194/wes-2018-71, in review, 2018.
    
    \item Simon, E., Gagne D.J., and Courtney, M.: Minute-Scale Wind Vector Forecasting Using Scanning Lidar Inputs to a Convolutional LSTM Neural Network, draft in preparation for submission to Atmospheric Measurement Techniques, 2019.
    
\end{enumerate}