%!TEX root = ../Thesis.tex
\chapter{Quote}
\label{sec:quote}
\bigskip
\setlength{\epigraphwidth}{1.0\textwidth}
\epigraph
{``Of all the forces of nature, I should think the wind contains the largest amount of motive power- that is, power to move things. Take any given space of the earth's surface- for instance, Illinois and all the power exerted by all the men, and beasts, and running-water, and steam, over and upon it, shall not equal the one hundredth part of what is exerted by the blowing of the wind over and upon the same space. And yet it has not, so far in the world's history, become proportionably valuable as a motive power. It is applied extensively, and advantageously, to sail-vessels in navigation. Add to this a few wind-mills, and pumps, and you have about all. That, as yet, no very successful mode of controlling, and directing the wind, has been discovered; and that, naturally, it moves by fits and starts- now so gently as to scarcely stir a leaf, and now so roughly as to level a forest- doubtless have been the insurmountable difficulties. As yet, the wind is an untamed, and unharnessed force; and quite possibly one of the greatest discoveries hereafter to be made will be the taming and harnessing of the wind. That the difficulties of controlling this power are very great is quite evident by the fact that they have already been perceived, and struggled with more than three thousand years; for that power was applied to sail-vessels, at least as early as the time of the prophet Isaiah.''\bigskip \bigskip \bigskip}
{Abraham Lincoln, Second Lecture on Discoveries and Inventions (1858)}

\begin{comment}
"Of all the forces of nature, I should think the wind contains the largest amount of motive power- that is, power to move things. Take any given space of the earth's surface- for instance, Illinois and all the power exerted by all the men, and beasts, and running-water, and steam, over and upon it, shall not equal the one hundredth part of what is exerted by the blowing of the wind over and upon the same space. And yet it has not, so far in the world's history, become proportionably valuable as a motive power. It is applied extensively, and advantageously, to sail-vessels in navigation. Add to this a few wind-mills, and pumps, and you have about all. That, as yet, no very successful mode of controlling, and directing the wind, has been discovered; and that, naturally, it moves by fits and starts- now so gently as to scarcely stir a leaf, and now so roughly as to level a forest- doubtless have been the insurmountable difficulties. As yet, the wind is an untamed, and unharnessed force; and quite possibly one of the greatest discoveries hereafter to be made will be the taming and harnessing of the wind. That the difficulties of controlling this power are very great is quite evident by the fact that they have already been perceived, and struggled with more than three thousand years; for that power was applied to sail-vessels, at least as early as the time of the prophet Isaiah."
-Abraham Lincoln, Second Lecture on Discoveries and Inventions (1858)
\end{comment}
%http://www.abrahamlincolnonline.org/lincoln/speeches/discoveries.htm